\documentclass[11pt,letterpaper]{article}
\usepackage{fontawesome5}
\usepackage[margin=1.2cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage[colorlinks=true, urlcolor=primaryColor]{hyperref}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{0.3cm}{0.2cm}
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\begin{document}

\begin{center}
    \Large\textbf{Khaled Rouissi}\\[0.2cm]
    \small
    Tunis, Tunisia \ | \ \href{mailto:khalidrouissi7@gmail.com}{khalidrouissi7@gmail.com} \ | \ \href{tel:+216-26-568-910}{+216 26 568 910}\\
    \href{https://linkedin.com/in/khalid-rouissi-6a136b242}{\faLinkedin Khalid Rouissi} \ | \ \href{https://github.com/KhalidRouissi1}{\faGithub Khalid Rouissi}
    \ | \ \href{https://leetcode.com/u/KhalidRouissi1/}{Leetcode: Khalid Rouissi}
\end{center}

\section{About Me}
Tunisian student who successfully completed Grade 1 of high school with distinction and chose to pursue a bachelor's degree at ISET Nabeul. Actively engaged in freelance projects that make a positive impact on people's lives. Former content creator from 2016 to 2018, with a passion for exploring and implementing cutting-edge technologies across various domains.

\section{Education}
\textbf{Higher Institute of Technological Studies of Nabeul}, Bachelor's in Computer Science (Sept 2022 – Present)\\
\textbf{Relevant Coursework:} Advanced Software Engineering, Data Structures and Algorithms, Web Development Technologies, Database Management Systems, Network Security, Mobile Application Development

\section{Experience}
\textbf{Internship}, Web Agency Tozeur (Jan 2023)
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Developed "WebCrafter," an innovative website creation tool using Golang for backend services and Next.js for the frontend interface.
\end{itemize}

\textbf{Internship}, Web Agency Tozeur (Jan 2022)
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Search for "Truss Solver" application for civil engineers, optimizing structural design processes.
    \item Created a dynamic hexagonal map using JavaScript, enhancing data visualization capabilities for client projects.
\end{itemize}

\section{Projects}
\textbf{NVS-Productivity-Manager} (Angular)
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Developed a comprehensive productivity tool featuring a customizable Pomodoro timer and interactive Kanban board.
   
\end{itemize}

\textbf{Microservice E-commerce Backend} (Spring Boot)
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Architecting a scalable e-commerce platform using microservices for improved modularity and performance.
    \item Implementing Kafka for event-driven architecture, MongoDB for flexible data storage, and Docker for containerization.
\end{itemize}

\textbf{Resume Builder} (React + Spring Boot)
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Created a dynamic resume generator with user authentication and customizable templates.
\end{itemize}

\textbf{Apple Website Clone} (Three.js + GSAP)
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Developed a visually stunning 3D showcase of the iPhone using Three.js for 3D rendering and animated with gsap.
    \item \href{https://apple-website-clone-3-d-animations.vercel.app/}{View Project}
\end{itemize}

\section{Social and Organizations}
Developed and implemented a comprehensive project for \textbf{La Voix de l'Enfant de Nabeul}, a non-profit organization supporting children without parents. The project aimed to streamline administrative processes and improve communication channels, enhancing the organization's ability to support vulnerable children.

\section{Skills}
\textbf{Languages:} Java, Go, PHP, JavaScript, TypeScript, Python, HTML5, CSS3\\
\textbf{Frameworks \& Libraries:} Spring Boot, Laravel, Django, Angular, React, Next.js, Express.js\\
\textbf{Tools \& Technologies:} Git, Docker, Kubernetes, PostgreSQL, MongoDB, Redis, Nginx, AWS, Firebase\\
\textbf{Methodologies:} Agile/Scrum, Test-Driven Development (TDD), Continuous Integration/Continuous Deployment (CI/CD)

\end{document}